--- 
title: "ALandClim"
author: "Forest Ecology ETH"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo
description: "This is a book about LandCLim"
---

# TOC


```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```



```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

Alternative index structure:


https://docs.google.com/document/d/1WsQXHRRXekKGCfXsGkc-zMnjEqkckcZ-CGNbogn2ptI/edit

ForClim overview
  What is ForClim?
    Model concept
    What ForClim does
    Who is behind ForClim
    History
    How to cite ForClim and this documentation
    Version and open access
    Main structure of this book
How Forclim works
  Tutorial with R
  Install ForClim
  Run ForClim
  Changning the ForClim setup
The source code


Forest stand scale processes






3.	Forest stand processes (i.e. within a grid cell)
  a.	Growth
    i.	Growth functions (?)
    ii.	Growth reducing factors
    b.	Mortality
    i.	Growth dependent
    ii.	Density dependent
    iii.	Maximum age
  c.	Establishment
  d.	Reproduction
  e.	Understory interactions

4.	Forest stand properties
  a.	Tree diameter (DBH)
  b.	Foliage weight
  c.	Twig weight
  d.	Bole weight
  e.	Dead biomass (fuel)
  f.	Leaf area index (LAI)
  g.	Light availability
  h.	Water availability 

5.	Landscape scale processes
  a.	Seed dispersal
  b.	Natural disturbances
    i.	Wind
    ii.	Fire
    iii.	Bark beetles
    iv.	Browsing
  c.	Management
    i.	Forest management
  1.	Thinning
  2.	Planting
  3.	Harvesting
    ii.	Meadow management
    iii.	Pasture management


